### 2012-04-30 trunk/GUIErrorDetector/paper/evaluation.tex
more edits to address reviewers' comments

We used a set of open-source projects from SourceForge, Google Code,
and the Eclipse plugin
marketplace as evaluation subjects. To choose subjects for each supported GUI framework,
we first searched for the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
in the above three source repositories, and then selected subjects based on the following
criteria. First, the subject must be a Java application, not
an open library. Second, the subject must use multithreading in its implementation.
Third, the subject must have undergone at least two years of active development,
and it is listed in the first 3 result pages based on popularity. This permits us
to exclude immature subjects that may contain obvious errors.

@@

We submitted all \newbugs new errors
to the subject developers. As of February 2012, 1 error in S3dropbox has been confirmed,
we have reproduced 4 errors, and 2 errors in FileBunker and ArecaBackup
had not yet been verified by the developers.

\begin{figure}[t]
\hspace{4mm}\small{In class: com.tomczarniecki.s3.gui.DeleteBucketAction}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
59.private void deleteBucket() \ttlcb
60.    executor.execute(new Runnable() \ttlcb
61.        public void run() \ttlcb
62.            try \ttlcb
63.                controller.deleteCurrentBucket();
64.            {\ttrcb} catch (Exception e) \ttlcb
65.                logger.info("Delete failed", e);
66.                deleteError(); 
67.            \ttrcb
68.       \ttrcb
69.    \ttrcb);
70.\ttrcb

@@

\begin{figure}[t]
\hspace{4mm}\small{In class: com.eclipserunner.views.impl.RunnerView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt} 
179.private void initializeResourceChangeListener() \ttlcb
180.  ResourcesPlugin.getWorkspace().addResourceChangeListener(
        new IResourceChangeListener() \ttlcb
181.      public void resourceChanged(IResourceChangeEvent event) \ttlcb
182.        refresh();
183.      \ttrcb
184.  \ttrcb, IResourceChangeEvent.POST\_CHANGE);
185.\ttrcb

@@

{\vspace{2mm}
\hspace{3mm}\small{In class: com.google.android.apps.mytracks.StatsUtilities}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
97.  public void setLatLong(int id, double d) \ttlcb
98.     TextView msgTextView = (TextView) activity.\textbf{findViewById}(id);
99.     msgTextView.setText(LAT\_LONG\_FORMAT.format(d));
100. \ttrcb
\end{alltt}
\end{CodeOut}}

@@

\noindent \textbf{\textit{Threats to validity.}}
There are two major threats to validity in our evaluation. 
One threat is the degree to which the subject programs
used in our experiment are representative of true practice.
In our evaluation, the studied subjects were selected with a bias towards popularity from
open-source repositories. Another threat is that we only employed three
widely-used call graph construction algorithms (i.e., RTA, 0-CFA, and 1-CFA) 
in our evaluation. Using other 
call graph construction algorithms such as XTA~\cite{xta} or VTA~\cite{Sundaresan:2000} 
 might achieve different results.

>>>>

We used a set of open-source projects from SourceForge, Google Code,
and the Eclipse plugin
marketplace as evaluation subjects. To choose subjects for each supported GUI framework,
we first searched for the framework keywords (e.g., ``Java Swing'' or ``Java SWT'')
in the above three source repositories, and then selected subjects based on the following
criteria. First, the subject must be a Java application, not
an open library. Second, the subject must use multithreading in its implementation.
Third, the subject is listed in the first 5 result pages.
This permits us to exclude immature subjects that may contain obvious errors.

@@

We submitted all \newbugs new errors
to the subject developers. As of April 2012, 1 error in S3dropbox has been confirmed,
we have reproduced 3 errors, and 3 errors in VirgoFTP, FileBunker and ArecaBackup
had not yet been verified by the developers.

\begin{figure}[t]
\hspace{4mm}{In class: com.tomczarniecki.s3.gui.DeleteBucketAction}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
59.private void deleteBucket() \ttlcb
60.    executor.execute(new Runnable() \ttlcb
61.        public void run() \ttlcb
62.            try \ttlcb
63.                controller.deleteCurrentBucket();
64.            {\ttrcb} catch (Exception e) \ttlcb
65.                logger.info("Delete failed", e);
66.                deleteError(); 
67.            \ttrcb
68.       \ttrcb
69.    \ttrcb);
70.\ttrcb

@@

\begin{figure}[t]
\hspace{4mm}{In class: com.eclipserunner.views.impl.RunnerView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt} 
179.private void initializeResourceChangeListener() \ttlcb
180.  ResourcesPlugin.getWorkspace().addResourceChangeListener(
        new IResourceChangeListener() \ttlcb
181.      public void resourceChanged(IResourceChangeEvent event) \ttlcb
182.        refresh();
183.      \ttrcb
184.  \ttrcb, IResourceChangeEvent.POST\_CHANGE);
185.\ttrcb

@@

{\vspace{2mm}
\hspace{3mm}{In class: com.google.android.apps.mytracks.StatsUtilities}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
97.  public void setLatLong(int id, double d) \ttlcb
98.     TextView msgTextView = (TextView) activity.\textbf{findViewById}(id);
99.     msgTextView.setText(LAT\_LONG\_FORMAT.format(d));
100. \ttrcb
\end{alltt}
\end{CodeOut}}

@@

\noindent \textbf{\textit{Threats to validity.}}
There are two major threats to validity in our evaluation. 
One threat is the degree to which the subject programs
used in our experiment are representative of true practice.
In our evaluation, we only selected studied subjects from
open-source repositories. Another threat is that we only employed three
widely-used call graph construction algorithms (i.e., RTA, 0-CFA, and 1-CFA) 
in our evaluation. Using other 
call graph construction algorithms such as XTA~\cite{xta} or VTA~\cite{Sundaresan:2000} 
 might achieve different results.

### 2012-04-30 trunk/GUIErrorDetector/paper/introduction.tex
more edits to address reviewers' comments

\begin{figure}[t]
\hspace{6mm}\small{In class: org.mozilla.gecko.gfx.LayerView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
68.  public LayerView(Context context, LayerController controller) \ttlcb
69.     super(context);
        ....
73.     mRenderer = new LayerRenderer(this);
74.     setRenderer(mRenderer);
        ...
     \ttrcb
\end{alltt}
\end{CodeOut}
\hspace{6mm} \small{In Android library class: android.opengl.GLSurfaceView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
272. public void setRenderer(Renderer renderer) \ttlcb
        ...
282.    mGLThread = new GLThread(renderer);
283.    mGLThread.start();   
     \ttrcb
\end{alltt}
\end{CodeOut}
 \hspace{6mm}\small{In class: org.mozilla.gecko.gfx.LayerRenderer}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
220. public void onSurfaceChanged(GL10 gl, int width, int height) \ttlcb
221.    gl.glViewport(0, 0, width, height);
222.    mView.setViewportSize(new IntSize(width, height));
     \ttrcb
\end{alltt}
\end{CodeOut}
\tinystep
\vspace*{-3.0ex} \Caption{{\label{fig:androiderror} 
Bug 703256 reported on 11/17/2011 in Fennec (Mozilla Firefox for Android)
release 10.0.a.rc3. On line 74, \CodeIn{LayerView}'s constructor
calls method \CodeIn{setRenderer} which 
spawns a new thread on line 283. This newly created, non-UI thread calls back method
\CodeIn{onSurfaceChanged} that accesses GUI objects on line 222 of \CodeIn{LayerRenderer},
causing an invalid thread access error. Our tool
finds this error and generates a report as shown in
Figure~\ref{fig:report}.
}} %\vspace{-5mm}
\end{figure}

@@

{\vspace{2mm}
\hspace{3mm}\small{In class: org.mozilla.gecko.gfx.LayerRenderer}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
220. public void onSurfaceChanged(GL10 gl, int width, int height) \ttlcb
221.     gl.glViewport(0, 0, width, height);
         \textbf{mView.post(new Runnable() \ttlcb}
             \textbf{public void run() \ttlcb}
222.             mView.setViewportSize(new IntSize(width, height));
             \textbf{\ttrcb}
         \textbf{\ttrcb);}
     \ttrcb
\end{alltt}
\end{CodeOut}}

@@

\begin{figure}[t]
\begin{CodeOut}
\begin{alltt}
   org.mozilla.gecko.gfx.LayerView.<init>(Context;LayerController)
-> android.opengl.GLSurfaceView.setRenderer(GLSurfaceView\$Renderer;)
-> java.lang.Thread.start()
-> android.opengl.GLSurfaceView\$GLThread.run()
-> android.opengl.GLSurfaceView\$GLThread.guardedRun()
-> org.mozilla.gecko.gfx.LayerRenderer.onSurfaceChanged(GL10;II)
-> org.mozilla.gecko.gfx.LayerView.setViewportSize(IntSize;)
   ... 
-> android.view.ViewRoot.recomputeViewAttributes(View;)
-> android.view.ViewRoot.checkThread()
\end{alltt}
\end{CodeOut}
%\hspace{5mm}\CodeIn{\scriptsize{org.mozilla.gecko.gfx.LayerView.<init>(Context;LayerController)}}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.opengl.GLSurfaceView.setRenderer(GLSurfaceView\$Renderer;)}}\\
%$\rightarrow$\CodeIn{ \scriptsize{java.lang.Thread.start()}}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.opengl.GLSurfaceView\$GLThread.run()}}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.opengl.GLSurfaceView\$GLThread.guardedRun()}}\\
%$\rightarrow$\CodeIn{ \scriptsize{org.mozilla.gecko.gfx.LayerRenderer.onSurfaceChanged(GL10;II)}}\\
%$\rightarrow$\CodeIn{ \scriptsize{org.mozilla.gecko.gfx.LayerView.setViewportSize(IntSize;)}}\\
%\hspace{5mm}\CodeIn{...}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.view.ViewRoot.checkThread()}}
\vspace*{-15pt}
\Caption{{\label{fig:report} Our tool reports
a method call chain that reveals the potential error in
Figure~\ref{fig:androiderror}. $\rightarrow$ represents
the call relationship
between methods, and \CodeIn{checkThread} is an Android library
method  that checks whether the current thread is the
event dispatching thread before accessing a GUI object.
8 more methods in the call chain, shown as
``\CodeIn{\small{...}}" above, are omitted for brevity.
}} %\vspace{-5mm}
\end{figure}

Our static analysis formulates finding invalid thread access as a call graph reachability
problem. Given a call graph, our technique traverses
paths from its entry nodes, checking whether
any path accesses a GUI object from a non-UI thread. If 
a suspicious path is found, the static analysis warns of a potential error.
The warning is in the form of a method
call chain from the starting point.
As an example, Figure~\ref{fig:report} shows a report produced
by our static analysis for the buggy code in Figure~\ref{fig:androiderror}.
This report clearly indicates how a new, non-UI thread is spawned and
accesses GUI objects. The generated report allows  developers to
inspect the method call chain, understand how the error
could be triggered, and fix it if it is a real bug.

@@

\item \textbf{Implementation.} We implemented our technique and
instantiated it for four
popular GUI frameworks: SWT, Eclipse plugin, Swing, and Android (Section~\ref{sec:implementation}). Our
tool implementation is publicly available at
{\smaller\url{http://guierrordetector.googlecode.com}}.

>>>>

\begin{figure}[t]
\hspace{6mm}{In class: org.mozilla.gecko.gfx.LayerView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
68.  public LayerView(Context context, LayerController controller) \ttlcb
69.     super(context);
        ....
73.     mRenderer = new LayerRenderer(this);
74.     setRenderer(mRenderer);
        ...
     \ttrcb
\end{alltt}
\end{CodeOut}
\hspace{6mm} {In Android library class: android.opengl.GLSurfaceView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
272. public void setRenderer(Renderer renderer) \ttlcb
        ...
282.    mGLThread = new GLThread(renderer);
283.    mGLThread.start();   
     \ttrcb
\end{alltt}
\end{CodeOut}
 \hspace{6mm}{In class: org.mozilla.gecko.gfx.LayerRenderer}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
220. public void onSurfaceChanged(GL10 gl, int width, int height) \ttlcb
221.    gl.glViewport(0, 0, width, height);
222.    mView.setViewportSize(new IntSize(width, height));
     \ttrcb
\end{alltt}
\end{CodeOut}
\tinystep
\vspace*{-3.0ex} \Caption{{\label{fig:androiderror} 
Bug 703256 reported on 11/17/2011 in Fennec (Mozilla Firefox for Android)
release 10.0.a.rc3. On line 74, \CodeIn{LayerView}'s constructor
calls method \CodeIn{setRenderer} which 
spawns a new thread on line 283. This newly created, non-UI thread calls back method
\CodeIn{onSurfaceChanged} that accesses GUI objects on line 222 of \CodeIn{LayerRenderer},
causing an invalid thread access error. Our tool
finds this error and generates a report as shown in
Figure~\ref{fig:report}.
}} %\vspace{-5mm}
\end{figure}

@@

{\vspace{2mm}
\hspace{3mm}{In class: org.mozilla.gecko.gfx.LayerRenderer}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
220. public void onSurfaceChanged(GL10 gl, int width, int height) \ttlcb
221.     gl.glViewport(0, 0, width, height);
         \textbf{mView.post(new Runnable() \ttlcb}
             \textbf{public void run() \ttlcb}
222.             mView.setViewportSize(new IntSize(width, height));
             \textbf{\ttrcb}
         \textbf{\ttrcb);}
     \ttrcb
\end{alltt}
\end{CodeOut}}

@@

\begin{figure}[t]
\begin{CodeOut}
\begin{alltt}
   org.mozilla.gecko.gfx.LayerView.<init>(Context;LayerController)
-> android.opengl.GLSurfaceView.setRenderer(GLSurfaceView\$Renderer;)
-> java.lang.Thread.start()
-> android.opengl.GLSurfaceView\$GLThread.run()
-> android.opengl.GLSurfaceView\$GLThread.guardedRun()
-> org.mozilla.gecko.gfx.LayerRenderer.onSurfaceChanged(GL10;II)
-> org.mozilla.gecko.gfx.LayerView.setViewportSize(IntSize;)
   ... 
-> android.view.ViewRoot.recomputeViewAttributes(View;)
-> android.view.ViewRoot.checkThread()
\end{alltt}
\end{CodeOut}
%\hspace{5mm}\CodeIn{\scriptsize{org.mozilla.gecko.gfx.LayerView.<init>(Context;LayerController)}}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.opengl.GLSurfaceView.setRenderer(GLSurfaceView\$Renderer;)}}\\
%$\rightarrow$\CodeIn{ \scriptsize{java.lang.Thread.start()}}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.opengl.GLSurfaceView\$GLThread.run()}}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.opengl.GLSurfaceView\$GLThread.guardedRun()}}\\
%$\rightarrow$\CodeIn{ \scriptsize{org.mozilla.gecko.gfx.LayerRenderer.onSurfaceChanged(GL10;II)}}\\
%$\rightarrow$\CodeIn{ \scriptsize{org.mozilla.gecko.gfx.LayerView.setViewportSize(IntSize;)}}\\
%\hspace{5mm}\CodeIn{...}\\
%$\rightarrow$\CodeIn{ \scriptsize{android.view.ViewRoot.checkThread()}}
\vspace*{-15pt}
\Caption{{\label{fig:report} Our tool reports
a method call chain that reveals the potential error in
Figure~\ref{fig:androiderror}. $\rightarrow$ represents
the call relationship
between methods, and \CodeIn{checkThread} is an Android library
method  that checks whether the current thread is the
event dispatching thread before accessing a GUI object.
8 more methods in the call chain, shown as
``\CodeIn{{...}}" above, are omitted for brevity.
}} %\vspace{-5mm}
\end{figure}

Our static analysis formulates finding invalid thread access as a call graph reachability
problem. Given a call graph, our technique traverses
paths from its entry nodes, checking whether
any path accesses a GUI object from a non-UI thread. If 
a suspicious path is found, the static analysis warns of a potential error.
The warning is in the form of a method
call chain from the starting point.
As an example, Figure~\ref{fig:report} shows a report produced
by our static analysis for the buggy code in Figure~\ref{fig:androiderror}.
This report indicates how a new, non-UI thread is spawned and
accesses GUI objects. The generated report allows  developers to
inspect the method call chain, understand how the error
could be triggered, and fix it if it is a real bug.

@@

\item \textbf{Implementation.} We implemented our technique and
instantiated it for four
popular GUI frameworks: SWT, Eclipse plugin, Swing, and Android (Section~\ref{sec:implementation}). Our
implementation is publicly available at
{\url{http://guierrordetector.googlecode.com}}.
